---
title: "**Homework 4**"
author: "Kevin Ha"
date: "September 39, 2021"
output: html_document
---
---

### **Problem 6.58**

##### 6.58 (a)
Given $z = 1.77$

$H_a: \mu > \mu_0 = P(Z \geq 1.77) = 1 - P(Z \leq 1.77)$

```{r, echo = FALSE}
p_val <- pnorm(1.77)
p_val
```

$1 - P(Z \leq 1.77)$ = $`r 1 - p_val`$

\

##### 6.58 (b)
$H_a: \mu > \mu_0 = P(Z \leq 1.77)$

$P(Z \leq 1.77)$ = $`r p_val`$

\

##### 6.58 (c)
$H_a: \mu \neq \mu_0 = 2P(Z \geq 1.77)$

$2P(Z \geq 1.77)$ = $`r 2*(1-p_val)`$

\

### **Problem 6.59**
##### 6.59 (a)
Given $z = -1.69$

$H_a: \mu > \mu_0 = P(Z \geq -1.69) = 1 - P(Z \leq -1.69)$

```{r, echo = FALSE}
p_val <- pnorm(-1.69)
p_val
```

$1 - P(Z \leq -1.69)$ = $`r 1 - p_val`$

\

##### 6.59 (b)
$H_a: \mu > \mu_0 = P(Z \leq -1.69)$

$P(Z \leq -1.69)$ = $`r p_val`$

\

##### 6.59 (c)
$H_a: \mu \neq \mu_0 = 2P(Z \geq -1.69)$

$2P(Z \geq -1.69)$ = $`r 2*(1-p_val)`$

\

### **Problem 6.71**
##### 6.71 (a)
Given $\overline{x} = 127.8$ and $\sigma = 30$

Test statistic formula: $z = \frac{\overline{X} - \mu_0}{\sigma / \sqrt{n}}$

$z = \frac{127.8 - 115}{30 / \sqrt{25}} = `r (127.8 - 115) / (30 / sqrt(25))`$

```{r}
p_val = pnorm(2.13)
p_val 
```

$H_a: \mu > 115 = 1 - P(Z \leq 2.1\overline{3}) = `r 1 - p_val`$

**The calculated p-value is very small and thus concludes that older students that have better attitudes towards school do end up getting better SSHA scores.**

\

##### 6.71 (b)
**The two important assumptions are that there is a SRS and there is a normal distribution of the data. SRS is more important, as normal distribution doesn't influence since there isn't any assumed skewdness or outliers within the data.**

### **Problem 6.73**
##### 6.73 (a)
$H_0:$ $\mu = 0$ mpg  
$H_a:$ $\mu \neq 0$ mpg

##### 6.73 (b)
Given $\sigma = 30$, $n = 20$, $\mu_0 = 0$, $\overline{X} = 2.73$

```{r}
x = c(5.0, 6.5, -0.6, 1.7, 3.7, 4.5, 8.0, 2.2, 4.9, 3.0, 4.4, 0.1, 3.0, 1.1, 1.1, 5.0, 2.1, 3.7, -0.6, -4.2)
mean(x)
```

$z = \frac{2.73 - 0}{3.0 / \sqrt{20}} = `r (2.73 - 0) / (3.0 / sqrt(20))`$

```{r}
p_val = pnorm(4.07)
p_val 
```

$H_a: 2(1 - P(Z < 4.07)) = `r 2 * (1 - p_val)`$

**The P-value is extremely small which indicates that the calculations are different.**

\

### **Problem 6.99**
##### 6.99 (a)
$n = 100$

$z = \frac{2453.7 - 2403.7}{880 / \sqrt{100}} = `r (2453.7 - 2403.7) / (880 / sqrt(100))`$

```{r}
p_val = pnorm(0.57)
p_val 
```

$H_a: 1 - P(Z < 0.72) = `r (1 - p_val)`$

\

##### 6.99 (b)
$n = 500$

$z = \frac{2453.7 - 2403.7}{880 / \sqrt{100}} = `r (2453.7 - 2403.7) / (880 / sqrt(500))`$

```{r}
p_val = pnorm(1.27)
p_val 
```

$H_a: 1 - P(Z < 0.72) = `r (1 - p_val)`$

\

##### 6.99 (c)
$n = 2500$

$z = \frac{2453.7 - 2403.7}{880 / \sqrt{100}} = `r (2453.7 - 2403.7) / (880 / sqrt(2500))`$

```{r}
p_val = pnorm(2.84)
p_val 
```

$H_a: 1 - P(Z < 0.72) = `r (1 - p_val)`$

\

### **Problem 6.120**



