---
title: "**Homework 6**"
author: "Kevin Ha"
date: "October 29, 2021"
output: html_document
---

---

### **Problem 9.37**

##### Problem 9.37a

```{r, echo = FALSE}
tab <- matrix(c(51, 6, 57, 12, 5, 17, 4, 1, 5, 67, 12, 79), ncol=3, byrow=TRUE)
colnames(tab) <- c('Number allowed','Number not allowed', 'Total')
rownames(tab) <- c('Small','Medium','Large', 'Total')
tab <- as.table(tab)
tab
```

\

##### Problem 9.37b

Not allowed in Small Stratum: $\frac{6}{57} = `r 6/57 * 100`$%

Not allowed in Medium Stratum: $\frac{5}{17} = `r 5/17 * 100`$%

Not allowed in Large Stratum: $\frac{1}{5} = `r 1/5 * 100`$%

\

##### Problem 9.37c
Medium and large need to be combined as the expected count for the large stratum/not allowed is too small (< 5) and cannot be used for the $\chi^2$ significance test.

\

##### Problem 9.37d
$H_0:$ There is no association between the size of the claim and the whether the claim is fraudulent or not.

\

##### Problem 9.37e
Calculating chi-squared manually:

```{r, echo = FALSE}
tab2 <- matrix(c(51, 6, 16, 6), ncol=2, byrow=TRUE)
colnames(tab2) <- c('Number allowed','Number not allowed')
rownames(tab2) <- c('Small','Large')
tab2 <- as.table(tab2)
tab2


print('Expected counts')

tab3 <- matrix(c(((67*57) / 79), ((12*57) / 79), ((67*22) / 79), ((12*22) / 79)), ncol=2, byrow=TRUE)
colnames(tab3) <- c('Number allowed','Number not allowed')
rownames(tab3) <- c('Small','Large')
tab3 <- as.table(tab3)
tab3


tab4 <- matrix(c((51-48.341772)^2 / 48.341772, (6-8.658228)^2 / 8.658228, (16 -  18.658228)^2 / 18.658228, (6-3.341772)^2 /3.341772), ncol=2, byrow=TRUE)
colnames(tab4) <- c('Number allowed','Number not allowed')
rownames(tab4) <- c('Small','Large')
tab4 <- as.table(tab4)
tab4

```

$\chi^2 = `r 0.1461712 + 0.8161227 +0.3787164 + 2.1144998`$

$df = (r - 1)(c - 1) = (2 - 1)(2 - 1) = 1$

$P$-value:

```{r}
pchisq(3.456, df = 1, lower.tail = FALSE)
```

\

### Problem 9.38

##### Problem 9.38a

Total number of claims not allowed:

Small: $\frac{6}{57} * 3342 = `r (6/57) * 3342`$

Medium: $\frac{5}{17} * 246 = `r (5/17)*246`$

Large: $\frac{1}{5} * 58 = `r 1/5 * 58`$

\

##### Problem 9.38b

$SE_{estimate} = SE_{sample-proportion} * (2n)$

Margin of error for Small Claims:

$SE \hat{p}_{small} = \sqrt{\frac{\hat{p}(1-\hat{p})}{n}} * 2(n) = \sqrt{\frac{0.11(0.89)}{3342}} * 2(3342) = `r sqrt((0.11*0.89) / 3342) * (2*3342)`$

$MoE_{small} = 351.7894737 \pm 36.1763348$ 

\

Margin of error for Medium Claims:

$SE \hat{p}_{medium} = \sqrt{\frac{\hat{p}(1-\hat{p})}{n}} * 2(n) = \sqrt{\frac{0.29(1-0.29)}{246}} * 2(246) = `r sqrt((0.29*0.71) / 246) * (2*246)`$

$MoE_{small} = 72.3529412 \pm 14.2339594$ 

\

Margin of error for Large Claims:

$SE \hat{p}_{large} = \sqrt{\frac{\hat{p}(1-\hat{p})}{n}} * 2(n) = \sqrt{\frac{0.20(1-0.20)}{58}} * 2(58) = `r sqrt((0.20*0.80) / 58) * (2*58)`$

$MoE_{small} = 11.6 \pm 6.0926185$ 



\

### Problem 9.50

Probability for Interval (1):

```{r, echo = FALSE}
pnorm(-0.60, lower.tail = TRUE)
```

Probability for Interval (2):

```{r, echo = FALSE}
pnorm(-0.10, lower.tail = TRUE) - pnorm(-0.60, lower.tail = TRUE)
```

Probability for Interval (3):

```{r, echo = FALSE}
pnorm(0.1, lower.tail = TRUE) - pnorm(-0.10)
```

Probability for Interval (4):

```{r, echo = FALSE}
pnorm(0.6) - pnorm(0.10)
```
Probability for Interval (5):

```{r, echo = FALSE}
pnorm(0.6, lower.tail = FALSE)
```

Expected Counts:

Interval (1): $0.274*500 = `r 0.274*500`$

Interval (2): $0.186*500 = `r 0.186*500`$

Interval (3): $0.080*500 = `r 0.080*500`$

Interval (4): $0.186*500 = `r 0.186*500`$

Interval (5): $0.274*500 = `r 0.274*500`$

\

Goodness of Fit Test:

$\chi^2 = \Sigma\frac{(obs-exp)^2}{exp}$

$\frac{(139-137)^2}{137} + \frac{(102-93)^2}{93} + \frac{(41-40)^2}{40} + \frac{(78-93)^2}{93} + \frac{(140-137)^2}{137} = `r (139-137)^2 / 137 + (102-93)^2 / 93 + (41-40)^2 / 40 + (78-93)^2 / 93 + (140-137)^2 / 137`$

Degrees of Freedom = $5-1 = 4$

P-value:
```{r}
pchisq(3.41, df = 4, lower.tail = FALSE)
```

\

**Summary:** Since the p-value is high, we fail to reject the null hypothesis and thus the random numbers follow a standard normal distribution.


### Problem 9.51

Intervals used:

1. Less than or equal to 0.32
2. Less than or equal to 0.60
3. Greater than 0.40 and less than or equal to 0.60
4. Greater than -0.70 and less than or equal to -0.10
5. Greater than 1.10

```{r}
x = rnorm(500)

obs1 = length(which(x <= 0.32))
exp1 = pnorm(0.32, mean(x), sd(x)) * 500

obs2 = length(which(x <= 0.60))
exp2 = pnorm(0.60, mean(x), sd(x)) * 500

obs3 = length(which(x <= 0.60 & x > 0.40))
exp3 = (pnorm(0.60, mean(x), sd(x)) - pnorm(0.40, mean(x), sd(x)))*500 

obs4 = length(which(x <= -0.10 & x > -0.70))
exp4 = (pnorm(-0.10, mean(x), sd(x)) - pnorm(-0.70, mean(x), sd(x)))*500 

obs5 = length(which(x > 1.10))
exp5 = pnorm(1.10, mean(x), sd(x), lower.tail = FALSE) * 500

```

Goodness of Fit Test:

$\chi^2 = \Sigma\frac{(obs-exp)^2}{exp}$

```{r, echo = FALSE}
k = (obs1-exp1)^2 / exp1 + (obs2-exp2)^2 / exp2 + (obs3-exp3)^2 / exp3 + (obs4-exp4)^2 / exp4 + (obs5-exp5)^2 / exp5
```

$\chi^2 = `r k`$


Degrees of Freedom = $5-1 = 4$

P-value:
```{r}
pchisq(k, df = 4, lower.tail = FALSE)
```