---
title: '**Homework 1**'
author: "Kevin Ha"
date: "September 2nd, 2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

---

### **Problem 1**

##### *Problem 1.1*
```{r echo=FALSE, hist-side, fig.show="hold", out.width="50%"}
x = c(0.2, 1.2, 0.9, 2.2, 3.2, 0.3, 1.7, 3.1, 2.3, 1.5, 2.5, 3.0, 2.6, 9.0)   
hist(x)
   
y = c(1.1, 2.3, 1.1, 3.6, 0.1, 1.0, 6.9, 4.8, 6.5, 7.8, 5.8, 8.0, 9.4, 9.8)   
hist(y) 
```

##### *Problem 1.2*
```{r}
summary(x)
var(x)
summary(y)
var(y)
```

```{r echo=FALSE, box-side, fig.show="hold", out.width="50%"}
boxplot(x, main="Boxplot of x", horizontal=TRUE, sub = "The only outlier is 9")
boxplot(y, main="Boxplot of y", horizontal=TRUE, sub = "There are no outliers")
```
\

##### *Problem 1.3*
```{r echo=FALSE, fig.align='center', out.width="50%"}
plot(x,y)
```
```{r}
cor(x,y)
```


<center>**The correlation coefficient presents that there is neither a weak or strong linear association between $x_i$ and $y_i$**</center>
\

##### *Problem 1.4*
Yes, the outlier is the pair **(9.0, 9.8)** since the first coordinator (x) was previously identified as an outlier for all $x_i$'s.

Removing the pair produces the following correlation coefficient:
```{r echo=FALSE}
a = c(0.2, 1.2, 0.9, 2.2, 3.2, 0.3, 1.7, 3.1, 2.3, 1.5, 2.5, 3.0, 2.6)   
b = c(1.1, 2.3, 1.1, 3.6, 0.1, 1.0, 6.9, 4.8, 6.5, 7.8, 5.8, 8.0, 9.4)

cor(a,b)
```
\

##### *Problem 1.5*
Upon removing the outlier in Problem 1.4, the correlation coefficient decreased and **weakened** the linear association between $x_i$ and $y_i$.

\

##### *Problem 1.6*
```{r echo=FALSE, qq-side, fig.show="hold", out.width="50%"}
qqnorm(x, main="Normal QQ Plot for x"); qqline(x)
qqnorm(y, main="Normal QQ Plot for y"); qqline(y)
```
<center>**The QQ plot of $x_i$'s is most likely of normal distribution as there is minimal deviation from the straight diagonal line in contrast to the plot of $y_i$'s**</center>

### Problem 2
Given that $F$ is the cdf for the random variable $X$, $F^{-1}(\alpha)$ is the inverse cdf or quantile function which determines the x value that is needed to achieve the probability $\alpha$.
With this in mind, the following probabilities can be determined:

$P(X \leq F^{-1}(\alpha/2)) = \alpha/2$ \
$P(X \leq F^{-1}(1-\alpha/2)) = 1 - \alpha/2$ \
$P(F^{-1}(\alpha/2) \leq X \leq F^{-1}(1 - \alpha/2)) = (1 - \alpha/2 - \alpha/2) = 1 - \frac{2\alpha}{2} = 1 - \alpha$ \

Given that $X \sim N(0,1)$ this establishes that X is normally distributed with a $\mu = 0$ and $\sigma = 1$, which is a standard normal distribution.

To calculate the following `qnorm()` and `pnorm()` will be used with $\mu = 0$ and $\sigma = 1$

\

$P (X \leq z_{0.05})$

```{r}
pnorm(qnorm(0.05, 0, 1))

```

$P (X \leq z_{0.05}) = 0.05$

\

$P (X \leq z_{1-0.05/2})$

```{r}
pnorm(qnorm(1-0.025, 0, 1))

```
$P (X \leq z_{1-0.05/2}) = 0.975$

\

$P (z_{0.05/2} \leq X \leq z_{1-0.05/2})$

\

$P (X \leq z_{0.05/2})$
```{r}
pnorm(qnorm(0.05/2, 0, 1))

```

\

$P (z_{0.05/2} \leq X \leq z_{1-0.05/2}) = 0.975 - 0.025 = 0.95$


### Problem 3

Verify using algebraic manipulation: 
$$ \frac{1}{n} \sum_{i=1}^{n} (x_i - \overline{x})^2 = \frac{1}{n} \sum_{i=1}^{n} x_i^2 - \overline{x}^2$$ 
1. Expand out $\frac{1}{n} \sum_{i=1}^{n} (x_i - \overline{x})^2$ to $\frac{1}{n} \sum_{i=1}^{n} (x_i^2 - 2x_i\overline{x} + \overline{x})$ \
2. $\frac{1}{n} \sum_{i=1}^{n} (x_i^2 - 2x_i\mu + \overline{x})$ is equivalent to $\frac{\sum_{i=1}^{n} x_i^2 - 2\overline{x}\sum_{i=1}^{n} x_i + \overline{x}^2 \sum_{i=1}^{n} 1} {n}$ \
3. $\sum_{i=1}^{n} 1$ is the same as adding 1, $n$ times and can be reduced to just $n$.  \
4. Simplified more: $\frac{\sum_{i=1}^{n} x_i^2}{n} - \frac{2\overline{x}\sum_{i=1}^{n} x_i}{n} + \frac{\overline{x}^2 n}{n}$ \
5. $\frac{\sum_{i=1}^{n} x_i}{n}$ is the sample mean and can be rewritten $\overline{x}$ \
6. Lastly, the simplifications result in: $\frac{\sum_{i=1}^{n} x_i^2}{n} - 2\overline{x}^2 + \overline{x}^2 = \frac{1}{n}{\sum_{i=1}^{n} x_i^2} - \overline{x}^2$, verifying equivalency.


