---
title: "**Homework 2**"
author: "Kevin Ha"
date: "September 12, 2021"
output: html_document
---

---

### **Problem 1**

\ 

##### Problem 1.1

Given $p = 0.4$ and $P(N \leq 8.25)$:


```{r}
pbinom(q = 8.25, size = 20, prob = 0.4)
pbinom(q = 8.25, size = 30, prob = 0.4)
pbinom(q = 8.25, size = 50, prob = 0.4)
pbinom(q = 8.25, size = 75, prob = 0.4)
pbinom(q = 8.25, size = 100, prob = 0.4)
```

\

##### Problem 1.2
```{r, echo = FALSE}
laplace_calculate <- function(num_trials) {
  result <- (8.25 - (num_trials * 0.4)) / sqrt(num_trials * 0.4 *(1-0.4))
  return(result)
}
```
Laplace theorem equation: $P(N \leq x) \approx \Phi\bigg(\frac{x - np}{\sqrt{np(1-p)}}\bigg)$

`laplace_calculate` is a function that calculates $\Phi\bigg(\frac{x - np}{\sqrt{np(1-p)}}\bigg)$ and takes a parameter `num_trials`:
```{r}
pnorm(laplace_calculate(num_trials = 20))
pnorm(laplace_calculate(num_trials = 30))
pnorm(laplace_calculate(num_trials = 50))
pnorm(laplace_calculate(num_trials = 75))
pnorm(laplace_calculate(num_trials = 100))
```

\

##### Problem 1.3
```{r}
accurate_vector <- c(0.5955987, 0.09401122, 0.0002305229, 1.826106e-08, 5.431127e-13)
approx_vector <- c(0.5454243, 0.08112525, 0.0003470073, 1.475701e-07, 4.557597e-11)
error_vector <- abs(accurate_vector - approx_vector)
error_vector
```

```{r, echo = FALSE, fig.align = 'center'}
plot(error_vector, main = "Scatter plot of errors for approximations", xlab = 'Index of Error Vector', ylab = 'Absolute Difference')
```

\

##### Problem 1.4
**Based on the scatter plot above, it can be said that the Laplace theorem becomes more accurate to the actual probability as the number of trials increases.
Thus the larger the trials, the better the normal distribution can be used to approximate the binomial distribution.**

\

### **Problem 2**



