---
title: "**Homework 7**"
author: "Kevin Ha"
date: "September 21, 2021"
output: html_document
---

---


### **Problem 12.31**

##### Problem 12.31a

```{r, echo = FALSE}
Control <- c(5.3, 3.9, 16.5, -14.9, -0.3, -4.3, -30.4, -12.5,
-15.4, -19.5, -6.5, 13.4, -4.2, 6.9, 25.5, -0.3,-3.2, 1.9,
-6.6, -12.7, -1.2, -13.7, 14.3, 8.8, 6.8, -7.1, -9.9,
-5.6, 15.5, 4.8, 6.1, -4.9, 6.1, 6.6, -4.5)

Individual <- c(-6.8	,
-4.8	,
5.5	,
11.9	,
-9.0	,
-4.7	,
-9.1	,
-15.1	,
-1.6	,
-3.8	,
7.3	,
-6.3	,
12.4	,
-0.9	,
-1.9	,
-18.3	,
6.9	,
-17.8	,
10.4	,
-23.5	,
8.0	,
-5.7	,
0.5	,
-2.1	,
-5.0	,
-8.4	,
0.2	,
12.0	,
-5.6	,
-1.6	,
-10.7	,
-4.0	,
-11.0	,
-12.1	,
-15.1)

Group <- c(-11.4	,
-7.3	,
-19.8	,
-13.7	,
-9.0	,
-22.4	,
-9.6	,
1.1	,
-2.6	,
-0.4	,
-2.5	,
-1.0	,
-2.2	,
-32.1	,
-30.5	,
-4.1	,
-18.1	,
-5.5	,
-14.1	,
-18.2	,
-11.0	,
-19.0	,
3.1	,
-12.0	,
-24.4	,
-11.3	,
11.3	,
-5.2	,
-12.9	,
-18.6	,
19.4	,
-19.2	,
-23.9	,
-19.6	)

tab <- matrix(c(35, -1.01, 11.50, 34, -10.79, 11.14, 35, -3.71, 9.08), ncol=3, byrow=TRUE)
colnames(tab) <- c('Sample Size','Sample Mean', 'Sample Standard Deviation')
rownames(tab) <- c('Control','Group','Individual')
tab <- as.table(tab)
tab

```

\

##### Problem 12.31b

**Yes, because the largest standard deviation is less than twice the smallest. $(11.50 < 2(9.08))$**

\

##### Problem 12.31c

```{r, echo = FALSE, hist-side, fig.show="hold", out.width="50%"}

hist(Control)
hist(Individual)
hist(Group)

```

**We can be confident that the samples means are approximately normal as most of the groups appear symmetric from the histogram distribution and have a sample size > 15.**

### **Problem 12.32**
##### Problem 12.32a

```{r, echo = FALSE}
library(readxl)
loss <- read_excel("ex12-31loss.xls")
```

One way ANOVA:

$\bar{X} = \frac{(n_1\bar{X_1} + n_2\bar{X_2} + n_3\bar{X_3})}{(n_1 + n_2 + n_3)} = \frac{(35*-1.01 + 34*-10.79 + 35*-3.71)}{(35+34+35)} = -5.12$ 

$SSB = \sum^3_{i=1}n_i(\bar{X}_i - \bar{X})^2 = 35(-1.01 + 5.12)^2 + 34(-10.79 + 5.12)^2 + 35(-3.71 + 5.12)^2 = 1753.87`$

$SSE = \sum^3_{i=1}(n_i - 1)S^2_i = (35-1)(11.50)^2 + (34-1)(11.14)^2 + (35-1)(9.08)^2 = 11394.96$

$f = \frac{MSB}{MSE} = \frac{SSB/(k-1)}{SSE/(n-k)}= \frac{1753.87/(3-1)}{11394.96/(104-3)} = 7.77$

```{r}
pf(7.77, 2, 103, lower.tail = FALSE)
```

<!-- str(loss) -->
<!-- attach(loss) -->
<!-- tapply(loss$Loss, loss$Group, length) -->
<!-- tapply(loss$Loss, loss$Group, mean) -->
<!-- tapply(loss$Loss, loss$Group, var) -->
<!-- oneway.test(loss$Loss ~ loss$Group) -->

**Summary: Because of the p-value is less than 0.05, the null hypothesis can be rejected and thus the group population means are not all equal.**

\

##### Problem 12.32b
```{r}
model = aov(loss$Loss ~ loss$Group)
qqnorm(model$residual)
qqline(model$residual)
```

**Again, we can feel confident that the sample means are approximately normal as a vast majority of the residuals follow the straight diagonal line of the QQ-plot, indicating strong evidence of normality.**

\

##### Problem 12.32c
```{r, echo = FALSE}
library("agricolae")
modi = aov(loss$Loss ~ loss$Group)
comparison = LSD.test(modi, "loss$Group", p.adj="none", console = TRUE)
```

##### Problem 12.32d

**Based on the results of the (a), (b), (c), the analysis of variance was able to be used to determine that the groups do not share equal population means and the group incentive program is the group differing the most from the other two groups.**

\

### Problem 12.33

##### Problem 12.33a

```{r, echo = FALSE}
tab <- matrix(c(length(Control), mean(Control) / 2.2 , sd(Control) / 2.2, length(Group), mean(Group) / 2.2, sd(Group) / 2.2, length(Individual), mean(Individual) / 2.2, sd(Individual) / 2.2), ncol=3, byrow=TRUE)
colnames(tab) <- c('Sample Size','Sample Mean', 'Sample Standard Deviation')
rownames(tab) <- c('Control','Group','Individual')
tab <- as.table(tab)
tab
```

\

##### Problem 12.33b
```{r, echo = FALSE}
loss2 <- read_excel("ex12-31loss.xls")
loss2$Loss = loss2$Loss / 2.2

str(loss2)
tapply(loss2$Loss, loss2$Group, length)
tapply(loss2$Loss, loss2$Group, mean)
tapply(loss2$Loss, loss2$Group, var)
oneway.test(loss2$Loss ~ loss2$Group)
```

\

### Problem 12.41

##### Problem 12.41a
Asking for average of blue and green eye color: $(\mu_1 + \mu_4)/2$

$\psi_1 = \mu_2 - (\mu_1 + \mu_4) / 2$

\

##### Problem 12.41b
Looking up are the linear combinations of each eye color: $\mu_1 + \mu_2 + \mu_4$

Taking the average of the combination above and contrasting it with the looking down ($\mu_3$):

$\phi_2 = \frac{(\mu_1 + \mu_2 + \mu_4)}{3} - \mu_3$


### Problem 12.42

##### Problem 12.42a
