---
title: "**Homework 7**"
author: "Kevin Ha"
date: "September 21, 2021"
output: html_document
---

---


### **Problem 12.31**

##### Problem 12.31a

```{r, echo = FALSE}
Control <- c(5.3, 3.9, 16.5, -14.9, -0.3, -4.3, -30.4, -12.5,
-15.4, -19.5, -6.5, 13.4, -4.2, 6.9, 25.5, -0.3,-3.2, 1.9,
-6.6, -12.7, -1.2, -13.7, 14.3, 8.8, 6.8, -7.1, -9.9,
-5.6, 15.5, 4.8, 6.1, -4.9, 6.1, 6.6, -4.5)

Individual <- c(-6.8	,
-4.8	,
5.5	,
11.9	,
-9.0	,
-4.7	,
-9.1	,
-15.1	,
-1.6	,
-3.8	,
7.3	,
-6.3	,
12.4	,
-0.9	,
-1.9	,
-18.3	,
6.9	,
-17.8	,
10.4	,
-23.5	,
8.0	,
-5.7	,
0.5	,
-2.1	,
-5.0	,
-8.4	,
0.2	,
12.0	,
-5.6	,
-1.6	,
-10.7	,
-4.0	,
-11.0	,
-12.1	,
-15.1)

Group <- c(-11.4	,
-7.3	,
-19.8	,
-13.7	,
-9.0	,
-22.4	,
-9.6	,
1.1	,
-2.6	,
-0.4	,
-2.5	,
-1.0	,
-2.2	,
-32.1	,
-30.5	,
-4.1	,
-18.1	,
-5.5	,
-14.1	,
-18.2	,
-11.0	,
-19.0	,
3.1	,
-12.0	,
-24.4	,
-11.3	,
11.3	,
-5.2	,
-12.9	,
-18.6	,
19.4	,
-19.2	,
-23.9	,
-19.6	)

tab <- matrix(c(35, -1.01, 11.50, 34, -10.79, 11.14, 35, -3.71, 9.08), ncol=3, byrow=TRUE)
colnames(tab) <- c('Sample Size','Sample Mean', 'Sample Standard Deviation')
rownames(tab) <- c('Control','Group','Individual')
tab <- as.table(tab)
tab

```

\

##### Problem 12.31b

**Yes, because the largest standard deviation is less than twice the smallest. $(11.50 < 2(9.08))$**

\

##### Problem 12.31c

```{r, echo = FALSE, hist-side, fig.show="hold", out.width="50%"}

hist(Control)
hist(Individual)
hist(Group)

```

**We can be confident that the samples means are approximately normal as most of the groups appear symmetric from the histogram distribution and have a sample size > 15.**

### **Problem 12.32**
##### Problem 12.32a

```{r, echo = FALSE}
library(readxl)
loss <- read_excel("ex12-31loss.xls")
```

One way ANOVA:

$\bar{X} = \frac{(n_1\bar{X_1} + n_2\bar{X_2} + n_3\bar{X_3})}{(n_1 + n_2 + n_3)} = \frac{(35*-1.01 + 34*-10.79 + 35*-3.71)}{(35+34+35)} = -5.12$ 

$SSB = \sum^3_{i=1}n_i(\bar{X}_i - \bar{X})^2 = 35(-1.01 + 5.12)^2 + 34(-10.79 + 5.12)^2 + 35(-3.71 + 5.12)^2 = 1753.87`$

$SSE = \sum^3_{i=1}(n_i - 1)S^2_i = (35-1)(11.50)^2 + (34-1)(11.14)^2 + (35-1)(9.08)^2 = 11394.96$

$f = \frac{MSB}{MSE} = \frac{SSB/(k-1)}{SSE/(n-k)}= \frac{1753.87/(3-1)}{11394.96/(104-3)} = 7.77$

```{r}
pf(7.77, 2, 104-3, lower.tail = FALSE)
```

**Summary: Because of the p-value is less than 0.05, the null hypothesis can be rejected and thus the group population means are not all equal.**

\

##### Problem 12.32b

```{r, echo = FALSE, out.width="50%"}
model = aov(loss$Loss ~ loss$Group)
qqnorm(model$residual)
qqline(model$residual)
```

**Again, we can feel confident that the sample means are approximately normal as a vast majority of the residuals follow the straight diagonal line of the QQ-plot, indicating strong evidence of normality.**

\

##### Problem 12.32c

Testing statistic for comparing two means:

$T_{i,j} = \frac{\bar{X_i}- \bar{X_j}}{\sqrt{S^2_p(\frac{1}{n_i} + \frac{1}{n_j})}}$

Pooled sample variance:

$S^2_p = MSE = \frac{SSE}{n-k} = \frac{11394.96}{(104−3)} = 112.82$

\

$T_{Individual,Group} = \frac{-3.71 + 10.79}{\sqrt{112.82(\frac{1}{35} + \frac{1}{34})}} = 2.77$

$T_{Control,Individual} = \frac{-1.01 + 3.71}{\sqrt{112.82(\frac{1}{35} + \frac{1}{35})}} = 1.06$

$T_{Control,Group} = \frac{-1.01 + 10.79}{\sqrt{112.82(\frac{1}{35} + \frac{1}{35})}} = 3.82$

\

LSD for $T_{Individual,Group}$

```{r}
2*(1-pt(2.77, 104-3))
```

LSD for $T_{Control,Individual}$
```{r}
2*(1-pt(1.06, 104-3))
```

LSD for $T_{Control,Group}$
```{r}
2*(1-pt(3.82, 104-3))
```

\

##### Problem 12.32d

Based on the results of the (a), (b), (c) the null hypothesis
($H_0: \mu_1 = \mu_2 = \mu_3$) fails to be rejected when comparing the Control and Individual groups as the calculated LSD values is greater than 0.05, while the $H_0$ is rejected when comparing Control / Group & Individual & Group as both groups have a LSD value < 0.05.

\

### Problem 12.33

##### Problem 12.33a

```{r, echo = FALSE}
tab <- matrix(c(length(Control), mean(Control) / 2.2 , sd(Control) / 2.2, length(Group), mean(Group) / 2.2, sd(Group) / 2.2, length(Individual), mean(Individual) / 2.2, sd(Individual) / 2.2), ncol=3, byrow=TRUE)
colnames(tab) <- c('Sample Size','Sample Mean', 'Sample Standard Deviation')
rownames(tab) <- c('Control','Group','Individual')
tab <- as.table(tab)
tab
```

\

##### Problem 12.33b
One way ANOVA:

$\bar{X} = \frac{(n_1\bar{X_1} + n_2\bar{X_2} + n_3\bar{X_3})}{(n_1 + n_2 + n_3)} = \frac{(35*-0.46 + 34*-4.90 + 35*-1.69)}{(35+34+35)} = -2.33$ 

$SSB = \sum^3_{i=1}n_i(\bar{X}_i - \bar{X})^2 = 35(-0.46 + 2.33)^2 + 34(-4.90 + 2.33)^2 + 35(-1.69 + 2.33)^2 = 361.29`$

$SSE = \sum^3_{i=1}(n_i - 1)S^2_i = (35-1)(5.23)^2 + (34-1)(5.06)^2 + (35-1)(4.13)^2 = 2354.85`$

$f = \frac{MSB}{MSE} = \frac{SSB/(k-1)}{SSE/(n-k)}= \frac{361.29/(3-1)}{2354.85/(104-3)} = 7.75$

```{r}
pf(7.75, 2, 104-3, lower.tail = FALSE)
```

**Summary: Because of the p-value is less than 0.05, the null hypothesis can be rejected and thus the group population means are not all equal.**

\

### Problem 12.41

##### Problem 12.41a
Asking for average of blue and green eye color: $(\mu_1 + \mu_4)/2$

$\psi_1 = \mu_2 - (\mu_1 + \mu_4) / 2$

\

##### Problem 12.41b
Looking up are the linear combinations of each eye color: $\mu_1 + \mu_2 + \mu_4$

Taking the average of the combination above and contrasting it with the looking down ($\mu_3$):

$\psi_2 = \frac{(\mu_1 + \mu_2 + \mu_4)}{3} - \mu_3$

\

### Problem 12.42

##### Problem 12.42a

Eye Color Contrast:

$H_0: \psi_1 = 0$

$H_a: \psi_1 \neq 0$


Looking Contrast:

$H_0: \psi_2 = 0$

$H_a: \psi_2 \neq 0$

\

##### Problem 12.42b

<!-- Sample contrast formula:  -->
<!-- $C_{\psi} = \sum^k_{i=1} a_i\bar{X_i}$ -->

```{r, echo = FALSE}
tab <- matrix(c(67, 3.19, 1.75, 37, 3.72, 1.72, 41, 3.11, 1.53, 77, 3.86, 1.67), ncol=3, byrow=TRUE)
colnames(tab) <- c('Sample Size','Sample Mean', 'Sample Standard Deviation')
rownames(tab) <- c('Blue','Brown','Down', 'Green')
tab <- as.table(tab)
tab
```

$c_1 =  \mu_2 - (\mu_1 + \mu_4) / 2 = 3.72 - (3.19+3.86) / 2 = `r 3.72 - (3.19+3.86) / 2`$

$c_2 = \frac{(\mu_1 + \mu_2 + \mu_4)}{3} - \mu_3 = \frac{(3.19 + 3.72 + 3.86)}{3} - 3.11 = `r ((3.19 + 3.72 + 3.86) / 3) - 3.11`$

\

##### Problem 12.42c

Pooled sample variance:

$S^2_p = \sqrt{MSE} = \sqrt{\frac{SSE}{n-k}} = \sqrt{\frac{(67-1)(1.75)^2+(37-1)(1.72)^2+(41-1)(1.53)^2 + (77-1)(1.67)^2}{(221-4)}} =`r ((67-1)*(1.75)^2+(37-1)*(1.72)^2+(41-1)*(1.53)^2 + (77-1)*(1.67)^2)/(221-4)`$

Formula for standard error of c:

$SE_c = \sqrt{S_p^2\sum^3_{i=1}\frac{a_i^2}{\bar{x}_i}}$


$SE_{c_1} = \sqrt{2.83 *(\frac{(-1^2)}{37} + \frac{(1/2)^2}{67} + \frac{(-1/2)^2}{77}) } = 0.30$

$SE_{c_2} = \sqrt{2.83 *(\frac{(-1^2)}{41} + \frac{(1/3)^2}{67} + \frac{(-1/3)^2}{77} + \frac{(-1/3)^2}{37})} = 0.29$

##### Problem 12.42d

$t = \frac{c_{\psi}}{SE_c}$

For contrast (eye color):
$t_1 = \frac{0.195}{0.30} = 0.64$

```{r}
2*pt(0.64, 220 - 4, lower.tail = FALSE)
```

For contrast (looking):
$t_1 = \frac{0.48}{0.29} = 1.66$

```{r}
2*pt(1.66, 220 - 4, lower.tail = FALSE)
```


Conclusion:

For contrast (eye-color) we fail to reject the null hypothesis since the calculated p-value > 0.05, for the contrast (looking) we also fail to reject since the p-value is > 0.05.

\

##### Problem 12.42e

$df = 222 - 1 = 221$
```{r}
abs(qt(0.05 / 2, 221))
```

95% confidence interval for contrast (eye color):

$\psi_1: 0.195 \pm (1.97*0.30) = (-0.40, 0.79)$

95% confidence interval for contrast (looking):

$\psi_2: 0.48 \pm (1.97*0.29) = (-0.09, 1.05)$







